Programming

### 2020-08-10 docs/blog/blogposts/Programming.Rmd
Updating website for collapse 1.3.0.

ganyNA <- function(x, g, use.g.names = TRUE) {
  if(is.atomic(g) || !is.GRP(g)) g <- GRP(g, return.groups = use.g.names)
  if(use.g.names) setNames(ganyNACpp(x, g[[1L]], g[[2L]]), group_names.GRP(g, FALSE)) else
    ganyNACpp(x, g[[1L]], g[[2L]])
}

>>>>

ganyNA <- function(x, g, use.g.names = TRUE) {
  if(is.atomic(g) || !is.GRP(g)) g <- GRP(g, return.groups = use.g.names)
  if(use.g.names) setNames(ganyNACpp(x, g[[1L]], g[[2L]]), GRPnames(g, FALSE)) else
    ganyNACpp(x, g[[1L]], g[[2L]])
}
